---
title: "${rPackageName}: Getting Started"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{${rPackageName}: Getting Started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This will become the getting started vignette on a `pkgdown` site.

# Installation instructions

`${rPackageName}` is based on a java library and must have a working version of `Java` and `rJava` installed prior to installation. The following commands can ensure that your `rJava` installation is working.

```R
install.packages("rJava")
rJava::.jinit()
rJava::J("java.lang.System")$getProperty("java.version")
```
To install `${rPackageName}` in R:

```{r}
library(devtools)

# you can install from the local copy:
load_all("~/Git/${githubRepository}")

# or from your github repository:
# install_github("${githubOrganisation}/${githubRepository}")

library(${rPackageName})
```
# Usage

Instructions for your users...

__Hello world - Object oriented style__

```{r}
J = ${rPackageName}::JavaApi$get()
ex = J$BasicExample$new("test message")
ex$getMessage()
```

__Hello world - R functional style__

```{r}
${rPackageName}::greet("tester")
```